Analysis for Project

### 2021-11-15 analysis/analysis.Rmd

tbl %>%
  kbl(caption="Cross-tabulation of age and current grade of student") %>%
  kable_minimal()
```

>>>>

acs %>% 
  tabyl(age, current_grade) %>%
  mutate_if(is.numeric, format, big.mark=",") %>%
  kbl(caption="Cross-tabulation of age and current grade of student",
      align=c("l",rep("r",13))) %>%
  kable_paper() %>%
  column_spec(2, background=c(rep("#D3D3D3",2), rep("white", 14))) %>%
  column_spec(3, background=c("white", 
                              rep("#D3D3D3",2), 
                              rep("white", 13))) %>%
  column_spec(4, background=c(rep("white", 2), 
                              rep("#D3D3D3",2), 
                              rep("white", 12))) %>%
  column_spec(5, background=c(rep("white", 3), 
                              rep("#D3D3D3",2), 
                              rep("white", 11))) %>%
  column_spec(6, background=c(rep("white", 4), 
                              rep("#D3D3D3",2), 
                              rep("white", 10))) %>%
  column_spec(7, background=c(rep("white", 5), 
                              rep("#D3D3D3",2), 
                              rep("white", 9))) %>%
  column_spec(8, background=c(rep("white", 6), 
                              rep("#D3D3D3",2), 
                              rep("white", 8))) %>%
  column_spec(9, background=c(rep("white", 7), 
                              rep("#D3D3D3",2), 
                              rep("white", 7))) %>%
  column_spec(10, background=c(rep("white", 8), 
                               rep("#D3D3D3",2), 
                               rep("white", 6))) %>%
  column_spec(11, background=c(rep("white", 9), 
                               rep("#D3D3D3",2), 
                               rep("white", 5))) %>%
  column_spec(12, background=c(rep("white", 10), 
                               rep("#D3D3D3",2), 
                               rep("white", 4))) %>%
  column_spec(13, background=c(rep("white", 11), 
                               rep("#D3D3D3",2), 
                               rep("white", 3))) %>%
  column_spec(14, background=c(rep("white", 12), 
                               rep("#D3D3D3",2), 
                               rep("white", 2)))
```
